Functions and Relations

### 2023-10-21 rec08/paper.tex
fixed error
fixed name error
functions

  (Transitivity). Let $a, b, c$ be any integers.
  Assume that $a \cng b \mod{2}$ and that $b \cng c \mod{2}$.
  By definition, these two hypotheses assert that there are integers $n, m$ so that $a - b = 2n$ and $c - b = 2m$.
  We need to show that $\exists c.\,a - c = 2c$.
  Setting $c := n - m$ yields $2(n - m) = 2n - 2m = a - b - (c - b) = a - b - c + b = a - c$ as desired.
\end{proof}

@@

>>>>

  (Transitivity). Let $a, b, c$ be any integers.
  Assume that $a \cng b \mod{2}$ and that $b \cng c \mod{2}$.
  By definition, these two hypotheses assert that there are integers $n, m$ so that $a - b = 2n$ and $b - c = 2m$.
  We need to show that $\exists k.\,a - c = 2k$.
  Setting $k := n + m$ yields $2(n + m) = 2n + 2m = (a - b) + (b - c) = a - b + b - c = a - c$ as desired.
\end{proof}

@@

Intuitively, a function from a set $A$ to another set $B$ is a rule for assigning each element of $A$ a unique element of $B$.
